### 2016-12-28 README.Rmd
updated plots and code

In this example, we fit a support vector machine with a radial basis function kernel to the Pima Indians diabetes data. (See `?pima` for a brief explanation of the data.)
```{r, message=FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(kernlab)  # for fitting SVMs

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos). 
partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, chull = TRUE,
        train = pima)
```

@@

# Grid of tuning parameter values
xgb.grid <- expand.grid(
  nrounds = 500,
  max_depth = 1:6,
  eta = c(0.001, 0.01, 0.1, 0.2, 0.3, 0.5),
  gamma = 0, 
  colsample_bytree = 1,
  min_child_weight = 1,
  subsample = 1
)

# Tune a support vector machine (SVM) using a radial basis function kerel to
# the Pima Indians diabetes data. This may take a few minutes!
set.seed(103)  # for reproducibility
pima.xgb <- train(diabetes ~ ., data = pima, method = "xgbTree",
                  prob.model = TRUE, na.action = na.omit, trControl = ctrl,
                  tuneGrid = xgb.grid)

>>>>

In this example, we fit a support vector machine with a radial basis function kernel to the Pima Indians diabetes data. (See `?pima` for a brief explanation of the data.)
```{r, message=FALSE, warning=FALSE, fig.width=12, fig.height=4}
# Load required packages
library(kernlab)  # for fitting SVMs

@@

# Partial dependence of glucose and age on diabetes test result (neg/pos).
grid.arrange(
  partial(pima.svm, pred.var = "glucose", plot = TRUE, train = pima),
  partial(pima.svm, pred.var = "age", plot = TRUE, train = pima),
  partial(pima.svm, pred.var = c("glucose", "age"), plot = TRUE, train = pima),
  ncol = 3
)
```

@@

# Grid of tuning parameter values
xgb.grid <- expand.grid(
  nrounds = c(1000, 2000),
  max_depth = 2:4,
  eta = c(0.001, 0.01, 0.1),
  gamma = 0, 
  colsample_bytree = 1,
  min_child_weight = 1,
  subsample = c(0.5, 0.75, 1)
)

# Tune am XGBoost model to the Pima Indians diabetes data. This may take a few 
# minutes!
set.seed(103)  # for reproducibility
pima.xgb <- train(diabetes ~ ., data = pima, method = "xgbTree",
                  prob.model = TRUE, na.action = na.omit, trControl = ctrl,
                  tuneGrid = xgb.grid)
